MLH1 Data Report

### 2018-03-19 Main_Report.rmd
updated makeFile and added batch10 female

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12,14,16,22) ]
#7: PERC male, 12: KAZ female! (14:CAST female, fake data) 16:HMI female

>>>>

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7,14,16,22) ]
#7: PERC male, 12: KAZ female! (14:CAST female, fake data) 16:HMI female
